---
title: "Incarceration Data Visualization"
output: html_document
---
```{r echo=F, include=F, cache=T}
source("analysis.R")
```

# Summary
The data set I am analyzing contains incarceration information from
`r summary_info$min_year` to `r summary_info$max_year`. The data set contains
variables such as:\
\
`r summary_info$columns`\
\
I will only be looking at the prison and jail population in relation to by
gender. These data are collected for `r summary_info$num_states` states and
`r summary_info$num_counties` counties.

# Prison Proportion Trends
This chart shows the total prison population proportion for males and females.
```{r echo=F}
male_female_prison_prop_lines
```
\
Males are overwhelmingly the larger proportion in the population. However,
females are steadily increasing in proportion while males are steadily dropping.
\

# Female Male Comparison
However, males still largely outnumber females in prison populations. To view
this disparity. I retrieved the 2016 prison populations and grouped them by
sex.\
```{r echo=F}
female_male_prison_2016
```
\
As you can see, the chart shows that males are greatly outnumbering females.
This is only 2016 counts, but every year before this is also a large
difference.

# State Map Ratio
I wanted to see which states were the contributors to males dominating the
prison population. To do so I divided the males in prison by the females in
prison then grouped them by state. The areas in the map that are blank had no
information about them.
```{r echo=F}
state_ratio_map
```
\
This map shows that Texas and California were the largest contributors to males
in prison. However, this might be because these states just send more people to
jail in general so I created another map that contains the proportion of males
to females in jail.\
```{r echo=F}
state_incarcerations_rel_prop
```
\
Ah, now instead of most of the offending areas being in Texas and California, it
is now mostly in the North East region of the map.